For_Clark

### 2020-07-22 Rcode/For_Clark_MAX.Rmd
Max Code

Mean in Parks w/ New Data
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}

poly<-sf::st_as_sfc(nps) #converts to new type of poly

@@

out<-as.data.frame(empty_list)
out_mean<-as.data.frame(rowMeans(out)) #take mean of the assign list above

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change 94 and 100 based on the length of your filepaths - this selects just the year and month i.e. 20041008
  colnames(out_mean)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_means/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_mean, newname, row.names = FALSE) #save as csv

@@

#loads those .csv and makes into single df
list_dates = list.files(path="/Users/killion/output_means/", pattern="*.csv", full.names=TRUE) #same folder you saved above output

final_means<-list_dates %>%
  map(read_csv) %>%
  reduce(cbind)

#append park code
final_means<-data.frame(park=park_codes, final_means)

#save
write.csv(final_means, "/Users/killion/final_means2.csv", row.names = FALSE)

>>>>

Max in Parks w/ New Data (average within day - get max day for each month)
L71 will need to be hashed out when working with full data - it selects only the months which have data in our sample folder
L93 values need to change based on the length of your new filepath
```{r}
#where to get max function
install.packages("remotes")
remotes::install_github("ejanalysis/analyze.stuff", force=TRUE)
library(analyze.stuff)
library(exactextractr)
poly<-sf::st_as_sfc(nps) #converts to new type of poly

@@

out<-as.data.frame(empty_list)
out_max<-as.data.frame(rowMaxs(out)) #take mean of the assign list above

#write csv
  n<-substr(list_all[[i]][[j]],94,100) # !!!!!!!! you will have to change 94 and 100 based on the length of your filepaths - this selects just the year and month i.e. 20041008
  colnames(out_max)[1] <- n #give values column name based on month
   name<-paste0("/Users/killion/output_max/",n) #create empty folder to save to
    newname<-paste0(name, ".csv")
write.csv(out_max, newname, row.names = FALSE) #save as csv

@@

#loads those .csv and makes into single df
list_dates = list.files(path="/Users/killion/output_max/", pattern="*.csv", full.names=TRUE) #same folder you saved above output

library(tidyverse)
final_max<-list_dates %>%
  map(read_csv) %>%
  reduce(cbind)

#append park code
final_max<-data.frame(park=park_codes, final_max)

#save
write.csv(final_max, "/Users/killion/final_max.csv", row.names = FALSE)
